\documentclass[10pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.3em}
\setlist[itemize]{leftmargin=1.2em, topsep=0.15em, itemsep=0.05em, parsep=0em}

% Two-column-style section: left = heading, right = content
\newcommand{\cvsection}[2]{%
  \vspace{0.5em}%
  \noindent
  \parbox[t]{0.15\textwidth}{#1}%
  \hspace{1em}%
  \parbox[t]{0.83\textwidth}{#2}%
}

\begin{document}
\pagestyle{empty}

%----------------------------------------------------------
% HEADER
%----------------------------------------------------------

\begin{center}
  {\fontsize{12}{13}\selectfont \textbf{Mridu Prashanth}}\\[1.2em]
  \hrule
\end{center}

\noindent\makebox[\textwidth][s]{%
  \makebox[0.33\textwidth][l]{\href{https://mriduprashanth.github.io/}{https://mriduprashanth.github.io/}}%
  \makebox[0.33\textwidth][c]{West Lafayette, Indiana}%
  \makebox[0.33\textwidth][r]{+1 (765) 701-8584}%
}

\vspace{0.3em}

%==========================================================
% EDUCATION
%==========================================================

\cvsection{Education}{
\textbf{Purdue University}, West Lafayette, IN \hfill Aug 2022 -- May 2026\\
BS in Computer Science (Honors), BS in Mathematics; GPA: 3.83\\
Relevant Courses: Computer Graphics, Linear Algebra, Artificial Intelligence, Machine Learning, Probability, Analysis of Algorithms, Data Structures, Programming in C, Systems Programming, Operating Systems, Randomized Algorithms\\
Research/Teaching Assistant; President (DOSA Club); TEDxPurdueU Design Chair; HelloWorld Hackathon Organizer; CS Corporate Partners Scholarship awardee; Dean's List \& Semester Honors
}

%==========================================================
% PAPERS & PUBLICATIONS (placeholder)
%==========================================================

\cvsection{Papers \& Publications}{
Placeholder text: Manuscripts in preparation. Will update upon submission.
}

%==========================================================
% ONGOING WORK (fills your active research entries)
%==========================================================

\cvsection{On-going Work}{
\textbf{VECMA-3SV: VE Complexity Management via Stochastic Single Shot Visibility} \hfill May 2025 -- Present\\
Advisor: Prof. Voicu Popescu, XR Lab, Purdue University\\
Compressed VEs by 80\%; developed an aggressive visible-set computation method with improved field-of-view coverage. Achieved error rates of 0.05\%, SSIM 0.99, PSNR 40dB. Built using C++/OpenGL/FLTK, Unity, Meta Quest 3. Delivered a talk at the Purdue Summer Research Symposium (2025).
}

%==========================================================
% PRESENTATIONS & POSTERS (placeholder)
%==========================================================

\cvsection{Presentations \& Posters}{
Placeholder text: Research posters and presentations forthcoming; will update after next symposium cycle.
}

%==========================================================
% RESEARCH EXPERIENCE
%==========================================================

\cvsection{Research Experience}{
\textbf{UFZs: A Novel Method to Identify Urban Fire Zones for Urban Planning} \hfill Jun 2024 -- Oct 2024\\
Advisors: Prof. Daniel Aliaga \& Prof. Aniket Bera, Purdue University\\
Modelled layouts using OpenStreetMaps and U-Tree datasets. Simulated fires in 10+ hotspot zones on Blender; analyzed wind/humidity factors. Applied K-Means, graph clustering, convex hull pipelines to identify hotspot types. Presented at Purdue Fall Research Expo (2024) and IDiF Summer Research Symposium (2024).\\[0.4em]

\textbf{AI-driven Robotic Triage Labeling \& Emergency Medical Information System} \hfill Jan 2024 -- May 2024\\
Advisor: Prof. Aniket Bera, IDEAS Lab\\
Evaluated SVM, MLP, Random Forest, Gaussian NB for patient acuity classification. Classified Level 1 acuity with 99\% accuracy. Utilized MIMIC-IV \& Yale EMD datasets. Augmented data using SMOTE and Google API embeddings. IEEE IROS 2024 submission; 2nd place at Purdue Spring Research Conference.\\[0.4em]

\textbf{AffectEcho: Emotion \& Affect Transfer for Speech Synthesis} \hfill Jun 2023 -- Dec 2023\\
Advisor: Prof. Aniket Bera, IDEAS Lab\\
AAAI 2024 submission. Achieved 5.4\% reduction in MCD compared to SOTA baselines. Built visualization tools using Python, Matplotlib, t-SNE.
}

%==========================================================
% TEACHING EXPERIENCE
%==========================================================

\cvsection{Teaching Experience}{
\textbf{Undergraduate Teaching Assistant, Department of Computer Science, Purdue} \hfill Aug 2023 -- Present\\
Courses: CS 381 (Algorithms), CS 252/240 (Systems Programming/C), CS 193 (Tools)\\
\begin{itemize}
  \item Lead developer: coordinated 4-person team; daily standups; designed homeworks \& solutions; built testing modules in C for 720 students.
  \item Led weekly labs/office hours; wrote quizzes; graded biweekly; supported $\sim$40 students per week.
  \item Taught pointers, memory allocation, threads, scripting languages, lex/yacc, algorithms, computational complexity, graph algorithms, and more using visuals and pseudocode.
\end{itemize}

\textbf{Tutor, WIE-WISP Program (College of Science, Purdue)} \hfill Aug 2023 -- Dec 2023\\
Tutored physics, calculus 1–3, precalc, Python, and C; reached $\sim$60 students.\\[0.4em]

\textbf{Officer \& Mentor, Girls Who Code (Purdue College Loop)} \hfill Jan 2023 -- May 2024\\
\begin{itemize}
  \item \textbf{Oakland Academy Workshop}: taught 30+ high school girls HTML/CSS/JS live on Code.org.
  \item \textbf{Jefferson High School Workshop}: created C/C++ materials; managed GWC LinkedIn page.
\end{itemize}
}

%==========================================================
% AWARDS
%==========================================================

\cvsection{Awards}{
CS Corporate Partners Scholarship; Dean’s List \& Semester Honors; Finalist at ICPC AlgoQueen National Collegiate Hackathon (2022).
}

%==========================================================
% PROJECTS
%==========================================================

\cvsection{Projects}{
\begin{itemize}
  \item \textbf{Bad Calculator 3000}: Converts infix to postfix and evaluates via stack; built with JavaScript/HTML/CSS.
  \item \textbf{SearchTracker}: Chrome extension to save papers and Google Scholar profiles.
  \item \textbf{NutritionAI}: ML-based nutritional estimation from images; built for HackMIT.
  \item \textbf{Pathways}: CS course-planning tool; built for BoilerMakeX.
  \item \textbf{AlgoQueen Hackathon Finalist}: Solved $\sim$30 algorithmic problems in C++.
\end{itemize}
}

%==========================================================
% COMMUNITY INVOLVEMENT (placeholder)
%==========================================================

\cvsection{Community Involvement}{
Placeholder text: STEM outreach, mentoring, and volunteering engagements to be added.
}

%==========================================================
% REFERENCES (placeholder)
%==========================================================

\cvsection{References}{
Available upon request.
}

\end{document}
